---
title: "Assessment1"
author: "Corinne Batho-Newton"
date: "25/01/2021"
output: word_document
---

```{r setup, include=FALSE}
library(ROAuth)
library("quanteda")
library("readtext")
library (streamR)
library(twitteR)
library(readr)
library(dplyr)
library("lubridate")
library("zoo")
require(quanteda)
require(readtext)
require(quanteda.corpora)
require(seededlda)
require(lubridate)
require(RColorBrewer)
require(dplyr)
require(ggplot2)
require(stm)

```

**-       Scraping tweets        -**
The last 3200 tweets from Stephen Morgan and Royston Smith

```{r}
# # Stephen Morgan
# SM_tweets <- get_timelines(c("StephenMorganMP"), n = 3200, parse=T, token=my_oauth)
# 
# save_as_csv(SM_tweets, "SMorganMP.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
# 
# 
# # Royston Smith
# RS_tweets <- get_timelines(c("Royston_Smith"), n = 3200, parse=T, token=my_oauth)
# 
# save_as_csv(RS_tweets, "RSmithMP.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")

```

**-       Setup Corpus'       -**
```{r}
MorganTweets <- read.csv("SMorganMP.csv")
SmithTweets <- read.csv("RSmithMP.csv")
MorganTexts <- readtext("SMorganMP.csv", text_field = "text")
SmithTexts <- readtext("RSmithMP.csv", text_field = "text")

SMorganCorpus <- corpus(MorganTexts)
RSmithCorpus <- corpus(SmithTexts)

```

**-       Cleaning        -**

Removing meta data from Stephen Morgan
```{r}
SMorganCorpus$retweets<-docvars(SMorganCorpus, "retweet_count")

library("lubridate")
Sys.setlocale("LC_TIME", "en_UK.UTF-8")
SMorganCorpus$date_time <- docvars(SMorganCorpus, "created_at")
SMorganCorpus$time <- as.POSIXct(SMorganCorpus$date_time, tz = "UTC", format = "%a
%b %d %H:%M:%S %z %Y")

SMorganCorpus$date <- as.Date(SMorganCorpus$time)
SMorganCorpus$month <- as.numeric(format(SMorganCorpus$date, format="%m"))
SMorganCorpus$year <- as.numeric(format(SMorganCorpus$date, format="%Y"))

library("zoo")
SMorganCorpus$yr_m <- as.yearmon(paste(SMorganCorpus$year, SMorganCorpus$month), "%Y %m")


```

Removing meta data from Royston Smith
```{r}
RSmithCorpus$retweets<-docvars(RSmithCorpus, "retweet_count")

library("lubridate")
Sys.setlocale("LC_TIME", "en_UK.UTF-8")
RSmithCorpus$date_time <- docvars(RSmithCorpus, "created_at")
RSmithCorpus$time <- as.POSIXct(RSmithCorpus$date_time, tz = "UTC", format = "%a
%b %d %H:%M:%S %z %Y")

RSmithCorpus$date <- as.Date(RSmithCorpus$time)
RSmithCorpus$month <- as.numeric(format(RSmithCorpus$date, format="%m"))
RSmithCorpus$year <- as.numeric(format(RSmithCorpus$date, format="%Y"))

library("zoo")
RSmithCorpus$yr_m <- as.yearmon(paste(RSmithCorpus$year, RSmithCorpus$month), "%Y %m")
```

**-       Summary       -**

Smith - longest tweet
```{r}
tokeninfoRS <- summary(RSmithCorpus, n=12916)
write.csv(tokeninfoRS, file="tokeninfoRS.csv", row.names=FALSE)
longesttweet <- tokeninfoRS[which.max(tokeninfoRS$Tokens), ]
texts(RSmithCorpus)[1453]
```
Morgan
```{r}
tokeninfoSM <- summary(SMorganCorpus, n=12916)
write.csv(tokeninfoSM, file="tokeninfoRS.csv", row.names=FALSE)
longesttweet <- tokeninfoSM[which.max(tokeninfoSM$Tokens), ]
texts(SMorganCorpus)[longesttweet[1,1]]
```

#  Comparing Proflic-ness by date
```{r fig.show='hide'}
library(dplyr)

tokeninfocollapsed <- tokeninfoRS %>%
  group_by(yr_m)%>%
  summarize(sum(Tokens)) %>%
  rename (Tokens = `sum(Tokens)`)

if (require(ggplot2)) ggplot(data = tokeninfocollapsed, aes(x = yr_m, y = Tokens)) +
  geom_line() + geom_point() + theme_bw()
```

Key-words in context - comparing use of tweets containing "covid"
```{r}
covidtweetsRS <- kwic(RSmithCorpus, pattern = "*covid*", window = 3)
covidtweetsSM <- kwic(SMorganCorpus, pattern = "*covid*", window = 3)

write.csv(covidtweetsRS, file="covidtweetsRS.csv")
write.csv(covidtweetsSM, file="covidtweetsSM.csv")

 kwic(RSmithCorpus, pattern = "*covid*", window = 3)
 kwic(SMorganCorpus, pattern = "*covid*", window = 3)
```

Converting to dfm
```{r}
dfmSmith <- dfm(RSmithCorpus)
dfmSmith
dfmMorgan<- dfm(SMorganCorpus)
dfmMorgan

#top features of each
# topfeatures(dfmSmith, 10)

dfmSmith_trimmed<- dfm(RSmithCorpus, remove = c(stopwords("english"),"rt", "@*", "+",
                                               "<","u",">","€","™","s" ,"0001f3fb", 
                                               "0001f3fb", "*â*","0001f447", "t" ),
                       stem = TRUE, remove_punct = TRUE, tolower=T, 
                       remove_symbols = T, remove_numbers = T, remove_url = T)

# topfeatures(dfmSmith_trimmed, 50)

dfmMorgan_trimmed<- dfm(SMorganCorpus, remove = c(stopwords("english"), 
                                              "rt","@*","+","<","u",">","€","™",
                                               "s","0001f3fb","0001f3fb","*â*",
                                               "0001f447", "iâ" ),
    stem = TRUE, remove_punct = TRUE, tolower=T, remove_symbols = T, 
    remove_numbers = T, remove_url = T)

# topfeatures(dfmMorgan_trimmed, 50)
```

term frequency - Inverse Document Frequency Weighting
```{r}
dfmMorgan_tfidf<- SMorganCorpus %>%
  dfm(remove = c(stopwords("english"),"rt","@","rt", "@*", "+", "<", "u", ">", "€", 
                 "™", "s","0001f3fb", "0001f3fb", "*â*","0001f447", "t"), 
      stem = TRUE, remove_punct = TRUE, tolower=T) %>%
  dfm_tfidf( scheme_tf = "count", scheme_df = "inverse",base = 10)

dfmSmith_tfidf<- RSmithCorpus %>%
  dfm(remove = c(stopwords("english"),"rt","@","rt", "@*", "+", "<", "u", ">", "€", 
                 "™", "s","0001f3fb", "0001f3fb", "*â*","0001f447", "t"), 
      stem = TRUE, remove_punct = TRUE, tolower=T) %>%
  dfm_tfidf( scheme_tf = "count", scheme_df = "inverse",base = 10) 


```

##  Wordclouds
```{r}
# textplot_wordcloud(dfmMorgan_tfidf, min_count = 6, random_order = FALSE, rotation = 0.25,
#     color = RColorBrewer::brewer.pal(8, "Dark2"))
# 
# textplot_wordcloud(dfmSmith_tfidf, min_count = 6, random_order = FALSE, rotation = 0.25,
#     color = RColorBrewer::brewer.pal(8, "Dark2"))

```


Creating master corpus dfm
```{r}
MasterCorpus <- RSmithCorpus+SMorganCorpus

MasterCorpus$author<-docvars(MasterCorpus, "screen_name")

dfm_Master<- MasterCorpus %>%
  dfm(remove = c(stopwords("english"),"rt", "@*", "+","<","u",">","€","™","s" 
                 ,"0001f3fb","0001f3fb", "*â*","0001f447", "t"), 
      stem = TRUE, 
      remove_punct = TRUE, tolower=T) %>%
      dfm_group(groups = "author") %>%
      dfm_weight(scheme = "prop")

write.csv(convert(dfm_Master, to="data.frame"), file="dfm_group.csv", row.names=FALSE)
```
Plot word frequency comparison

```{r}
dfm_Master_Grouped<-dfm_sort(dfm_Master)

dfm_Master_Grouped2<-textstat_frequency(
  dfm_Master,
  n = 30,
  groups = "author")

#plot for comparison (using dfm with top 20th ranked words only)

ggplot(data = dfm_Master_Grouped2, aes(x = factor(nrow(dfm_Master_Grouped2):1), y = frequency)) +
    geom_point() +
    facet_wrap(~ group, scales = "free") +
    coord_flip() +
    scale_x_discrete(breaks = nrow(dfm_Master_Grouped2):1,
                       labels = dfm_Master_Grouped2$feature) +
    labs(x = NULL, y = "Relative frequency")

```

##      Text analysis - Topic modelling

LDA probabilistic model
```{r}
# tmod_ldaMS <- textmodel_lda(dfmMorgan_tfidf, k = 10)
# tmod_ldaRS <- textmodel_lda(dfmSmith_tfidf, k = 10)
```
 Morgan top 20
```{r}
# seededlda::terms(tmod_ldaMS, 20)
```
Royston top 20
```{r}
# seededlda::terms(tmod_ldaRS, 20)
```

Further Cleaning & Stemming
```{r}
dfmMorgan_tfidf_stem<- dfm(SMorganCorpus, 
                           remove = c(stopwords("english"),"rt", "@*", "+", "<", "u",
                                      ">", "€","™","s", "0001f3fb", "0001f3fb",
                                      "*â*","0001f447", "t","0*"), 
                           stem=T,
  remove_punct = TRUE, remove_numbers = TRUE, remove_symbol = TRUE,tolower=T) %>% 
  dfm_tfidf(scheme_tf = "count", scheme_df = "inverse",base = 10) 

dfmSmith_tfidf_stem<- dfm(RSmithCorpus, 
                           remove = c(stopwords("english"),"rt", "@*", "+", "<", "u",
                                      ">", "€","™","s", "0001f3fb", "0001f3fb",
                                      "*â*","0001f447", "t","0*","fe0f"), 
                           stem=T,
  remove_punct = TRUE, remove_numbers = TRUE, remove_symbol = TRUE,tolower=T) %>% 
  dfm_tfidf(scheme_tf = "count", scheme_df = "inverse",base = 10) 
```

Re-apply model
```{r}
require(quanteda)
require(readtext)
require(quanteda.corpora)
require(seededlda)
require(lubridate)
require(RColorBrewer)
require(dplyr)
require(ggplot2)
require(stm)
tmod_ldaMS <- textmodel_lda(dfmMorgan_tfidf_stem, k = 12)
tmod_ldaRS <- textmodel_lda(dfmSmith_tfidf_stem, k = 9)
```

csv table
```{r}
topwords<-as.data.frame(seededlda::terms(tmod_ldaMS, 20))
write.csv(topwords, file="top_wordsSM.csv")
# View(topwords)


topwords<-as.data.frame(seededlda::terms(tmod_ldaRS, 20))
write.csv(topwords, file="top_wordsRS.csv")
# View(topwords)
```



```{r}


MorganTweets$topic <- seededlda::topics(tmod_ldaMS)
View(MorganTweets[,c(5,91)])

SmithTweets$topic <- seededlda::topics(tmod_ldaRS)
View(SmithTweets[,c(5,91)])

#attach the topic variable to the corpus object as well:
SMorganCorpus$topic <- seededlda::topics(tmod_ldaMS)
RSmithCorpus$topic <- seededlda::topics(tmod_ldaRS)

topics_tableM<-ftable(MorganTweets$topic)
# View(topics_tableM)
topicsprop_tableM<-as.data.frame(prop.table(topics_tableM))
# View(topicsprop_tableM)

topics_tableS<-ftable(SmithTweets$topic)
# View(topics_tableS)
topicsprop_tableS<-as.data.frame(prop.table(topics_tableS))
# View(topicsprop_tableS)


#visualise the topic frequencies

ggplot(data=topicsprop_tableM, aes(x=Var1, y=Freq)) + 
  geom_bar(stat = "identity") +
  theme_classic()+
  labs (x= "Topics", y = "Topic %")+
  labs(title = "Topic proportions - Stephen Morgan") +
  scale_x_discrete(labels=c("topic1" = "1 Local Issues", "topic2" = "2 Goverment Spending",
                            "topic3" = "3 Royal Navy", 
                            "topic4" = "4 Defense", "topic5"="5 Local Community",
                            "topic6" = "6 Healthcare", "topic7" = "7 Goverment Policies", 
                            "topic8" = "8 Green Campaigns", 
                            "topic9"="9 Social Inequality", 
                            "topic10" = "10 Election Campaings","topic11"="11 Schools",
                            "topic12" = "12 Local Support")) +
  theme(axis.text.x = element_text(face="bold", 
                           size=10, angle=45,hjust = 1)) +
  theme(text=element_text(size=12,  family="serif")) +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(data=topicsprop_tableS, aes(x=Var1, y=Freq)) + 
  geom_bar(stat = "identity") +
  theme_classic()+
  labs (x= "Topics", y = "Topic %")+
  labs(title = "Topic proportions - Royston Smith") +
  scale_x_discrete(labels=c("topic1" = "1 Brexit", "topic2" = "2 RAF", "topic3" = "3 Local Areas", 
                            "topic4" = "4 Expressions of appreciation", "topic5"="5 Current breifings",
                            "topic6" = "6 Achievements", "topic7"="7 Local Issues",
                            "topic8" = "8 Southampton Council", "topic9"="9 Healthcare")) +
  theme(axis.text.x = element_text(face="bold", 
                           size=10, angle=45,hjust = 1)) +
  theme(text=element_text(size=12,  family="serif")) +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
texts(SMorganCorpus)[28]
texts(SMorganCorpus)[696]
```

```{r}
texts(RSmithCorpus)[33]
texts(RSmithCorpus)[59]
```

